---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CausalModels

<!-- badges: start -->
<!-- badges: end -->

The goal of CausalModels is to provide a survey of fundamental causal inference models in one
single location. While there are many packages for these types of models, CausalModels brings
them all to one place with a simple user experience.

## Installation

You can install the development version of CausalModels from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ander428/CausalModels")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CausalModels)
library(causaldata)

data(nhefs)

nhefs.nmv <- nhefs[which(!is.na(nhefs$wt82)),]
nhefs.nmv$qsmk <- as.factor(nhefs.nmv$qsmk)

confounders <- c("sex", "race", "age", "education", "smokeintensity",
                 "smokeyrs", "exercise", "active", "wt71")

# initialize package
?init_params
init_params(wt82_71, qsmk,
            covariates = confounders,
            data = nhefs.nmv, simple = F)

# mode the causal effect of qsmk on wt82_71
model <- standardization(nhefs.nmv)
print(model)
summary(model)
```
